### 2020-01-23 defesa/tex/chapter/mcd.tex
wip

The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility. After a CLS is constructed, a complete search can be executed to find the best solution.

@@

\begin{equation}\label{eq:b_i}
B_i = A_i\cup\bigcup_{j=1}^n \{ 2\pi+\Gamma_-(i,j), 2\pi+\Gamma_+(i,j) \}.
\end{equation}
Assuming $B_i$ is sorted in ascending order, a copy of the elements of $A_i$ shifted to the interval $[2\pi, 4\pi]$ is added to its end and a simple traversal, going through the first element until the last one, simulates a traversal on the circular list $A_i$.
This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$. This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).

@@

    \caption{The intersections list of a disk with three other disks.}
	 %\input{tex/figures/array_disks.tex}
    \includegraphics[scale=.28]{tex/figures/3_disks_intersect2.pdf}
    \fautor
    \label{fig:array_disks}
\end{figure}

\begin{teorema}\label{lema:disk}
	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
\end{teorema}

@@

A simple adaptation can be done on \autoref{algoritmo:mcd_1} to make it return a CLS that contains an optimal solution of MCD for that disk. This is shown in \autoref{algoritmo:mcd_cls}. 
Notice also that MCD-1 is defined only for unit disks, however, this constrained can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius. A result about the runtime complexity of \autoref{algoritmo:mcd_cls} has already been given by \autoref{lema:disk}, the following result states about the adaption of it to be used in an algorithm for MCD.

>>>>

The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility. After a CLS is constructed, a complete search is executed to find the best solution. That is why, as an heuristic, it is a good idea to create small CLSs that somehow can still provide good solutions.

@@

\begin{equation}\label{eq:b_i}
B_i = A_i\cup\bigcup_{j=1}^n \{ 2\pi+\Gamma_-(i,j), 2\pi+\Gamma_+(i,j) \}.
\end{equation}
Assuming $B_i$ is sorted in ascending order, a copy of the elements of $A_i$ shifted to the interval $[2\pi, 4\pi]$ is added to its end and a simple traversal, going through the first element until the last one, simulates a traversal on the circular list $A_i$.
This works because for any pair of disks, such that $\Gamma_+(i,j) > \Gamma_-(i,j)$, $B_i$ will contain $\Gamma_-(i,j) < \Gamma_+(i,j) + 2\pi$. This is shown in \autoref{fig:array_disks}, where the list of intersection between $\partial D_1$ with circles $\partial D_2, \partial D_3$ and $\partial D_4$ is duplicated simulating a traversal in $B_i$ (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively).

@@

    \caption{The intersections list of a disk with three other disks.}
	 %\input{tex/figures/array_disks.tex}
    \includegraphics[scale=.3]{tex/figures/3_disks_intersect2.pdf}
    \fautor
    \label{fig:array_disks}
\end{figure}

\begin{theorem}\label{lema:disk}
	\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
\end{theorem}

@@

A simple adaptation can be done on \autoref{algoritmo:mcd_1} to make it return a CLS that contains an optimal solution of MCD for that disk. This is shown in \autoref{algoritmo:mcd_cls}. 
Notice also that MCD-1 is defined only for unit disks, however, this constraint can be dropped, as it is introduced just for the sake of keeping the text more simple and \autoref{algoritmo:mcd_1} works for any radius. A result about the runtime complexity of \autoref{algoritmo:mcd_cls} has already been given by \autoref{lema:disk}, the following result states about the adaption of it to be used in an algorithm for MCD.
